Manuscript plots

### 2023-12-05 manuscript_modelling_and_plots.Rmd
removing old plot code, changing figure number on code chunks

## Load fixations data

This dataframe contains an example fixation pattern for plotting Figure 4.

```{r}
# Setting digits to 15 mins that fixation duration s are not rounded to annoying precise values. 
options(digits = 15)
example.fixation <- fread(file = here::here("gaze_entropy_heterogenous/data/example.fixation.csv"))
```

@@

## Manuscript Figure 4 - fixations within their state spaces

An example of the fixations for a trial. This is to demonstrate the theory beyond gaze transition entropy. The order of the fixations are coloured to indicate their order. The probability of a fixation being in a state space given is it in the current one is used alongside the probability of the total distribution of fixations.

```{r}
# maximum pitch and yaw coordinates
maxY = max(example.fixation$pitch)
maxX = max(example.fixation$yaw)

# minimum pitch and yaw coordinates
minY = min(example.fixation$pitch)
minX = min(example.fixation$yaw)

# creating state spaces - cuts the x and y coordinates into 3 degree chunks 
example.fixation <- example.fixation %>%
  dplyr::mutate(x_range = cut(yaw, seq(minX, maxX, by = 10), right = FALSE)) %>%
  dplyr::mutate(y_range = cut(pitch, seq(minX, maxY, by = 10), right = FALSE))

# state space coordinates
state_space_coordinates <- example.fixation %>%
  dplyr::group_by(x_range, y_range) %>%
  dplyr::summarise(count = n()) %>%
  dplyr::ungroup()  %>%
  tidyr::complete(x_range, y_range) %>%
  dplyr::mutate(state_space = row_number()) %>%
  dplyr::mutate(x_range_2 = x_range, y_range_2 = y_range) %>%
  tidyr::separate_wider_delim(x_range, ",", names = c("x_lower", "x_upper")) %>%
  tidyr::separate_wider_delim(y_range, ",", names = c("y_lower", "y_upper")) %>%
  dplyr::mutate(x_lower = str_replace_all(x_lower, "\\[|\\]", ""), x_upper = str_replace_all(x_upper, "\\(|\\)", "")) %>%
  dplyr::mutate(y_lower = str_replace_all(y_lower, "\\[|\\]", ""), y_upper = str_replace_all(y_upper, "\\(|\\)", "")) %>%
  dplyr::mutate(x_lower = as.numeric(x_lower), x_upper = as.numeric(x_upper), y_lower = as.numeric(x_lower), y_upper = as.numeric(x_upper))

# plot the state space grids alongside the fixation coordinates 
fixation_state_space <- ggplot() +
  geom_vline(state_space_coordinates, mapping = aes(xintercept = x_upper), col = "grey") +
  geom_hline(state_space_coordinates, mapping = aes(yintercept = y_upper), col = "grey") +
  geom_vline(state_space_coordinates, mapping = aes(xintercept = x_lower), col = "grey") +
  geom_hline(state_space_coordinates, mapping = aes(yintercept = y_lower), col = "grey") +
  geom_point(example.fixation, mapping = aes(yaw, pitch, col = fixation_number), size = .6) +
  scale_colour_continuous(name = "Fixation number", type = "viridis", breaks = c(25, 75, 125)) +
  ylab("Pitch (°)") +
  xlab("Yaw (°)") +
  ylim(-20, 10) +
  xlim(-40, 40) +
  theme_plot +
  theme(legend.position = "bottom", legend.key.width = unit(1, 'cm'), legend.key.height = unit(.3, 'cm'))

# data saving   
ggsave(here::here("gaze_entropy_heterogenous/plots/Fig4.tiff"), plot = fixation_state_space , width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

## Manuscript Figure 5: Correlation between N-back performance and age

@@

# plot saving
ggsave(here::here("gaze_entropy_heterogenous/plots/Fig5.tiff"), plot = n_back_age_performance , width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

@@

## Manuscrip Figure 6 - Posterior distribution for mu parameters

@@

# saving final plot
ggsave(here::here("gaze_entropy_heterogenous/plots/Fig6.tiff"), plot = sge.plot, width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

## Manuscript Figure 7 - Posterior distribution for sigma parameters

@@

# saving plots
ggsave(here::here("gaze_entropy_heterogenous/plots/Fig7.tiff"), plot = sge.plot.sigma, width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

## Manuscript Figure 8: overlying raw data on posterior predicitive intervals

@@

# plot saving
ggsave(here::here("gaze_entropy_heterogenous/plots/Fig8.tiff"), plot = posterior.mean.intervals.sge, width = 16, height = 10, units = 'cm', dpi = 300, type = 'cairo')
```

## Manuscript Figure 9 part 1: Calculating heterogenity of the n-back effect for SGE

@@

## Manuscript 9 part 2: Proportion of population who has reduced SGE during n-back

@@

# data saving
ggsave(here::here("gaze_entropy_heterogenous/plots/Fig9.tiff"), plot = population.plot, width = 16, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

@@

## Manuscript Figure 10 - Visualing posterior distribution for mu parameters - GTE

@@

ggsave(here::here("gaze_entropy_heterogenous/plots/Fig10.tiff"), plot = gte.plot, width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

## Manuscript Figure 11 - Visualing posterior distribution for sigma parameters - GTE

@@

ggsave(here::here("gaze_entropy_heterogenous/plots/Fig11.tiff"), plot = sge.plot.sigma, width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

## Manuscript Figure 12: overlying raw data on posterior predicitive intervals for gaze transition entropy model

@@

ggsave(here::here("gaze_entropy_heterogenous/plots/Fig12.tiff"), plot = posterior.mean.intervals.gte, width = 16, height = 10, units = 'cm', dpi = 300, type = 'cairo')
```

## Manuscript Figure 13 part 1: Calculating heterogenity of the n-back effect for GTE

@@

## Manuscript Figure 13 part 2: proportion of population who follow average GTE

@@

ggsave(here::here("gaze_entropy_heterogenous/plots/Fig13.tiff"), plot = population.plot.gte, width = 16, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

## Manuscript Figure 14 part 1: Heterogenity effects of GTE on sigma parameters

@@

## Manuscript Figure 14 part 2: Proportion of population where sigma of GTE decreases in the presence of n-back

@@

ggsave(here::here("gaze_entropy_heterogenous/plots/Fig14.tiff"), plot = population.plot.sigma.gte, width = 16, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

## Manuscript figure 15 Stationary gaze entropy - influence of age on heteroenity effects

@@

ggsave(here::here("gaze_entropy_heterogenous/plots/Fig15.tiff"), plot = age.nback.effect.sge , width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

@@

ggsave(here::here("gaze_entropy_heterogenous/plots/Fig16.tiff"), plot = age.nback.effect.gte, width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

>>>>

@@

## Manuscript Figure 4: Correlation between N-back performance and age

@@

# plot saving
ggsave(here::here("gaze_entropy_heterogenous/plots/Fig4.tiff"), plot = n_back_age_performance , width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

@@

## Manuscrip Figure 5 - Posterior distribution for mu parameters

@@

# saving final plot
ggsave(here::here("gaze_entropy_heterogenous/plots/Fig5.tiff"), plot = sge.plot, width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

## Manuscript Figure 6 - Posterior distribution for sigma parameters

@@

# saving plots
ggsave(here::here("gaze_entropy_heterogenous/plots/Fig6.tiff"), plot = sge.plot.sigma, width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

## Manuscript Figure 7: overlying raw data on posterior predicitive intervals

@@

# plot saving
ggsave(here::here("gaze_entropy_heterogenous/plots/Fig7.tiff"), plot = posterior.mean.intervals.sge, width = 16, height = 10, units = 'cm', dpi = 300, type = 'cairo')
```

## Manuscript Figure 8 part 1: Calculating heterogenity of the n-back effect for SGE

@@

## Manuscript 8 part 2: Proportion of population who has reduced SGE during n-back

@@

# data saving
ggsave(here::here("gaze_entropy_heterogenous/plots/Fig8.tiff"), plot = population.plot, width = 16, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

@@

## Manuscript Figure 9 - Visualing posterior distribution for mu parameters - GTE

@@

ggsave(here::here("gaze_entropy_heterogenous/plots/Fig9.tiff"), plot = gte.plot, width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

## Manuscript Figure 10 - Visualing posterior distribution for sigma parameters - GTE

@@

ggsave(here::here("gaze_entropy_heterogenous/plots/Fig10.tiff"), plot = sge.plot.sigma, width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

## Manuscript Figure 11: overlying raw data on posterior predicitive intervals for gaze transition entropy model

@@

ggsave(here::here("gaze_entropy_heterogenous/plots/Fig11.tiff"), plot = posterior.mean.intervals.gte, width = 16, height = 10, units = 'cm', dpi = 300, type = 'cairo')
```

## Manuscript Figure 12 part 1: Calculating heterogenity of the n-back effect for GTE

@@

## Manuscript Figure 12 part 2: proportion of population who follow average GTE

@@

ggsave(here::here("gaze_entropy_heterogenous/plots/Fig12.tiff"), plot = population.plot.gte, width = 16, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

Not included in the manuscript, but plotting out some individuals with their gaze transition entropy as a function of lead vehicle. The reversal of the effect is stark in these drivers.

```{r}
ggplot(entropy.total %>%
         dplyr::filter(ppid == 31), mapping = aes(x = gte.norm, y = n_back)) +
  geom_jitter(height = .03)

ggplot(entropy.total %>%
         dplyr::filter(ppid == 17), mapping = aes(x = gte.norm, y = n_back)) +
  geom_jitter(height = .03)

ggplot(entropy.total %>%
         dplyr::filter(ppid == 43), mapping = aes(x = gte.norm, y = n_back)) +
  geom_jitter(height = .03)

ggplot(entropy.total %>%
         dplyr::filter(ppid == 21), mapping = aes(x = gte.norm, y = n_back)) +
  geom_jitter(height = .03)

ggplot(entropy.total %>%
         dplyr::filter(ppid == 9), mapping = aes(x = gte.norm, y = n_back)) +
  geom_jitter(height = .03)

ggplot(entropy.total %>%
         dplyr::filter(ppid == 3), mapping = aes(x = gte.norm, y = n_back)) +
  geom_jitter(height = .03)
```

## Manuscript Figure 13 part 1: Heterogenity effects of GTE on sigma parameters

@@

## Manuscript Figure 13 part 2: Proportion of population where sigma of GTE decreases in the presence of n-back

@@

ggsave(here::here("gaze_entropy_heterogenous/plots/Fig13.tiff"), plot = population.plot.sigma.gte, width = 16, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

## Manuscript figure 14 Stationary gaze entropy - influence of age on heteroenity effects

@@

ggsave(here::here("gaze_entropy_heterogenous/plots/Fig14.tiff"), plot = age.nback.effect.sge , width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```

@@

ggsave(here::here("gaze_entropy_heterogenous/plots/Fig15.tiff"), plot = age.nback.effect.gte, width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```
